Faithful Variable Screening for High-Dimensional Convex Regression

### 2016-03-14 tex/scam/faithful.tex
minor ref fixes
supplement correction

\begin{aug}
\author{\fnms{Min} \snm{Xu}\thanksref{t1,m1}\ead[label=e1]{min.cut@gmail.com}},
\author{\fnms{Minhua} \snm{Chen}\thanksref{m2}\ead[label=e2]{minhua@somewhere.com}}
\and
\author{\fnms{John} \snm{Lafferty}\thanksref{t1,m3}\ead[label=e3]{lafferty@galton.uchicago.edu}}

@@

\address{Address of M.~Chen\\
Amazon.com\\
410 Terry Avenue North\\
Seattle, Washington 98109\\
USA\\
\printead{e2}\\}

>>>>

\begin{aug}
\author{\fnms{Min} \snm{Xu}\thanksref{t1,m1}\ead[label=e1]{minx@wharton.upenn.edu}},
\author{\fnms{Minhua} \snm{Chen}\thanksref{m2}}
\and
\author{\fnms{John} \snm{Lafferty}\thanksref{t1,m3}\ead[label=e3]{lafferty@galton.uchicago.edu}}

@@

\address{Address of M.~Chen\\
Amazon.com\\
410 Terry Avenue North\\
Seattle, Washington 98109\\
USA}
